Analysis of NLA17 Dissolved Gas Indicator

### 2020-12-10 scripts/dgIndicatorAnalysis.Rmd
Amending layer in geopackage so need to use delete_layer = TRUE, append = TRUE

dg_1 <- select(dg,site.id:map.lon.dd, dissolved.co2, dissolved.ch4, dissolved.n2o, WSA9, WSA9_NAME)
names(dg_1)
dg_1 <- clean_names(dg_1) %>% filter(wsa9 != "AK") # underscores are "safer" names used in GIS
names(dg_1)
# To enable spatial analysis of the data, the dataframe will be converted to a 'simple features' (sf) object.
# Define coordinates
coords <- data.frame(longitude = dg_1$map_lon_dd, latitude = dg_1$map_lat_dd)

@@

dg_sf1 <- filter(dg_sf1, sample_source == "DG") # now 1219 obs vs. previously 1185 obs., why change in sample size
st_crs(dg_sf1)

@@

>>>>

dg_1 <- select(dg,site.id:map.lon.dd, dissolved.co2, dissolved.ch4, dissolved.n2o, co2.sat.ratio, ch4.sat.ratio, n2o.sat.ratio, WSA9, WSA9_NAME)
names(dg_1)
dg_1 <- clean_names(dg_1) %>% filter(wsa9 != "AK") %>% 
  mutate(log_n2o = round(log(dissolved_n2o),3)) %>% 
  mutate(log_n2osatratio = round(log(n2o_sat_ratio),3))
# underscores are "safer" names used in GIS

names(dg_1)
# To enable spatial analysis of the data, the dataframe will be converted to a 'simple features' (sf) object.
# Define coordinates
coords <- data.frame(longitude = dg_1$map_lon_dd, latitude = dg_1$map_lat_dd)

@@

dg_sf1 <- filter(dg_sf1, sample_source == "DG") # now 1184 obs vs. previously 1185 obs., why change in sample size
st_crs(dg_sf1)

@@

# N.B. b/c old layer with untransformed was already in geodatabase have to delete it and then append the new layer
st_write(dg_sf1, dsn = file.path(getwd(), "nladg_v1.gpkg"), layer = "dg_sf1", driver = "GPKG", delete_layer = TRUE, append = TRUE, quiet = FALSE)
st_layers("nla_dg1.gpkg")
